%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Pandiri Pramod} \\ \vspace{1pt}
    \small 856-997-3050 $|$ \href{mailto:pandiripramodreddy@gmail.com}{\underline{pandiripramodreddy@gmail.com}} $|$
    \href{https://www.linkedin.com/in/pramodreddypandiri/}{\underline{linkedin.com/in/pramodreddypandiri}} $|$
    \href{https://github.com/pramodreddypandiri}{\underline{github.com/pramodreddypandiri}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Full-stack Software Engineer with strong experience in Java, Spring Boot, Python, SQL, and React, specializing in high-performance APIs, low-latency backend systems, and scalable microservices. Proven ability to optimize data workflows, ensure reliability under peak loads, and deliver accurate, business-critical software in fast-paced environments. Passionate about building resilient systems for enterprise platforms.
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Cincinnati}{Cincinnati, OH}
      {Masters in Information Technology}{Dec 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{May 2025 -- Present}
      {Invision Global Tech Inc}{Remote}
      \resumeItemListStart
        \resumeItem{Built a payment intergration platform to support various payment gateways which increased userbase by 50\%} 
        \resumeItem{Reduced reconciliation failures from 20\% to under 3\% by implementing file-integrity checks with timestamp validation and configurable retry logic before processing gateway settlement CSVs.}
        \resumeItem{Engineered new solutions for API documentation effort by 80\% across 12 microservices by building a centralized LLM-powered generator that auto-parsed controller code from Git and produced OpenAPI specs via Velocity templates.}
        \resumeItem{Automated security vulnerability triage, reducing handling time by 70\% by developing a Spring Boot pipeline that auto-created Jira tickets, ServiceNow incidents, and Confluence remediation pages from scanner reports.}
        \resumeItem{Consolidated 15+ search APIs into a single generic endpoint adopted by 4 downstream apps, using XML-driven SQL templates, a facade routing layer, and a flexible criteria model.}
        \resumeItem{Improved transaction throughput by 40\% under peak load (500K+ daily) by refactoring the reconciliation batch pipeline to chunked parallel execution using Spring Batch partitioning.}
        \resumeItem{Reduced payment incident resolution time from 4 hours to under 45 minutes by building a real-time mismatch dashboard with Kafka-streamed alerts and automated Slack notifications to finance.}
        \resumeItem{Achieved 99.7\% cross-system payment matching accuracy across 3 gateways by building an idempotent matching engine with duplicate detection, partial-amount matching, and configurable tolerance thresholds.}
        \resumeItem{Decreased API response latency by 60\% (p95 from 1.2s to 480ms) by introducing Redis caching for settlement summaries, index tuning, and connection pool optimization across 12 microservices.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Sep 2024 -- May 2025}
      {University of Cincinnati}{Cincinnati, OH}
      \resumeItemListStart
        \resumeItem{Designed and deployed microservices for transactional systems using Java Spring Boot and PostgreSQL, reducing latency by 20\% in high-throughput operations.}
        \resumeItem{Implemented Kafka-based event-driven architecture for reliable data streaming and messaging between services, increasing system throughput.}
        \resumeItem{Developed responsive UI dashboards using React and Material UI, enabling real-time analytics for operational insights.}
        \resumeItem{Refactored JavaScript codebase to TypeScript, reducing runtime defects by 25\% and improving maintainability.}
        \resumeItem{Enhanced backend performance by optimizing PL/SQL and PostgreSQL queries, improving reporting and analytics speed by 15\%.}
        \resumeItem{Automated ETL workflows and database operations using Python and Shell scripting, reducing manual tasks by 40\%.}
        \resumeItem{Accelerated CI/CD pipelines using GitLab, Linux CLI, and Jenkins, cutting release cycles by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Developer}{Nov 2021 -- Aug 2023}
      {Tata Consultancy Services}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed enterprise-grade features for risk management and requirements engineering software, improving processing efficiency by 20\%.}
        \resumeItem{Implemented backend services with Java Servlets, Spring, and Hibernate, driving a 35\% increase in active user base.}
        \resumeItem{Supported ETL workflows and database operations with Python and Shell Scripting, reducing manual intervention by 40\%.}
        \resumeItem{Enhanced system performance by optimizing PL/SQL queries, accelerating report generation speed by 20\%.}
        \resumeItem{Accelerated CI/CD pipelines using GitLab, Linux CLI, and Jenkins, cutting release cycles by 30\%.}
        \resumeItem{Integrated Kafka messaging for distributed job execution, improving scalability for batch risk analytics.}
        \resumeItem{Introduced geolocation-based security controls, reinforcing compliance with export data governance.}
        \resumeItem{Collaborated in an Agile team environment, participating in code reviews and architecture discussions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, TypeScript, JavaScript (ES6+), SQL, Shell Scripting} \\
     \textbf{Frameworks}{: Spring Boot 3.x, Hibernate, Express.js, React, Node.js} \\
     \textbf{Backend}{: REST APIs, Microservices, Kafka, RabbitMQ, PL/SQL, PostgreSQL, MongoDB} \\
     \textbf{Cloud}{: Azure (App Services, AKS), AWS (EC2, S3, RDS), Docker, Kubernetes, Terraform} \\
     \textbf{DevOps}{: Git, GitLab CI/CD, Jenkins, Maven, SonarQube} \\
     \textbf{Testing}{: JUnit, Mockito, Jest, Mocha, Postman} \\
     \textbf{Monitoring}{: ELK Stack, Prometheus, Grafana} \\
     \textbf{Methodologies}{: Agile, Scrum, SDLC, Secure Coding Practices, N-tier Architecture, OOD}
    }}
 \end{itemize}


%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     AWS Certified Developer -- Associate $|$ Google AI Essentials $|$ Object Oriented Design (Coursera)
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
